\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-30 paper.qmd
Update section triangulation

Delaunay triangulation is used to connect neighboring centroids, which is needed to preserve neighborhood information when the model is lifted into \pD{}.

When $k = 2$ Delaunay triangulation on $C^{(2)}$ generates the model in \gD{} space, which is a triangular mesh (@fig-NLDR-scurve (d)). It generates convex hulls of $C^{(2)}$ such that the circumcircle of every triangle in the triangulation contains no other points from $C^{(2)}$.

When neighboring centroids are connected with edges in Delaunay triangulation in \gD{}, there are situations where distant centroids are also connected, which generates long edges. To generate a smooth surface in \gD{}, these long edges are removed (@fig-NLDR-scurve (d)).

>>>>

Delaunay triangulation [@lee1980] is used to connect neighboring centroids, which is needed to preserve neighborhood information when the model is lifted into \pD{}.

<!-- When $k = 2$ Delaunay triangulation on $C^{(2)}$ generates the model in \gD{} space, which is a triangular mesh (@fig-NLDR-scurve (d)). It generates convex hulls of $C^{(2)}$ such that the circumcircle of every triangle in the triangulation contains no other points from $C^{(2)}$. -->

It can also happen that distant centroids can be connected, which can result in long line segments. In order to generate a smooth surface in \gD{}, these long line segments must be removed (@fig-NLDR-scurve (d)).

### 2024-05-30 paper.tex
Update section triangulation

Delaunay triangulation is used to connect neighboring centroids, which
is needed to preserve neighborhood information when the model is lifted
into \pD{}.

When \(k = 2\) Delaunay triangulation on \(C^{(2)}\) generates the model
in \gD{} space, which is a triangular mesh (Figure~\ref{fig-NLDR-scurve}
(d)). It generates convex hulls of \(C^{(2)}\) such that the
circumcircle of every triangle in the triangulation contains no other
points from \(C^{(2)}\).

When neighboring centroids are connected with edges in Delaunay
triangulation in \gD{}, there are situations where distant centroids are
also connected, which generates long edges. To generate a smooth surface
in \gD{}, these long edges are removed (Figure~\ref{fig-NLDR-scurve}
(d)).

>>>>

Delaunay triangulation \citep{lee1980} is used to connect neighboring
centroids, which is needed to preserve neighborhood information when the
model is lifted into \pD{}.

It can also happen that distant centroids can be connected, which can
result in long line segments. In order to generate a smooth surface in
\gD{}, these long line segments must be removed
(Figure~\ref{fig-NLDR-scurve} (d)).
